HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-12 draft/ms_v1.tex
CModel: S/N

\subsubsection{Input magnitude and the $\mathrm{S}/\mathrm{N}$ of \cmodel{} photometry}

        \item In Fig \ref{fig:cmodel_sn}, we show the relations between the input
            magnitude and the $\mathrm{S}/\mathrm{N}$ recovered by \cmodel{}
            photometry in $g$- and $i$-band.

        \item \plan{Define $\mathrm{S}/\mathrm{N}$.
                    Unlike point sources, at fixed total magnitude, the
                    synthetic galaxies have a range of size and shape that
                    lead to different average surface brightness.
                    Comparing to stars, at the same input magnitude, synthetic
                    galaxies have lower average $\mathrm{S}/\mathrm{N}$ and larger
                    scatter. }

        \item \plan{Seeing condition still impacts the $\mathrm{S}/\mathrm{N}$ of
                    galaxies}

        \item \plan{Blendedness can reduce the $\mathrm{S}/\mathrm{N}$ a little.}

        \item \plan{Briefly discuss the detection limit of point sources.
            Basically consistent with the reported values in \citet{HSCDR1}.
            Although at $i{\sim}25.2$, the average $\mathrm{S}/\mathrm{N}$ is quite high,
            small fraction of galaxies will have very low $\mathrm{S}/\mathrm{N}$.}

>>>>

\subsubsection{Input magnitude and the \s2n{} of \cmodel{} photometry}

    In Fig \ref{fig:cmodel_sn}, we first show the relations between the input 
    magnitudes and the \s2n{} of the synthetic galaxies estimated by the ratio 
    between \cmodel{} flux and its uncertainties from \hscpipe{}. 
    Since these galaxies are extended objects, the \s2n{} here should be treated 
    as the average \s2n{} which is different from the \s2n{} of stars using PSF 
    photometry.

    We still use $i$- and $g$-band as examples. 
    Comparing to the similar figure for stars, the most obvious difference is that
    at fixed input magnitude, the \s2n{} distribution of galaxies show much larger
    scatter than stars.  
    At the same total flux, galaxy can have different size and shape, and 
    naturally leads to differences in their peak and average \s2n{}.  
    This also makes it difficult to have a clear definition of ``detection limit'' 
    for galaxies. 
    For $i$-band, the typical \s2n{} for synthetic galaxies at the magnitude limit 
    of our sample ($25.2$ mag) is ${\sim}20$, but the low-\s2n{} tail has already 
    reached to the \s2n{}$=5$ boundary.  
    This suggests that, although HSC Wide can detect galaxies as faint as 
    $i{\sim}26.0$ mag, the sample will become highly incomplete. 
    Furthermore, it can also introduce bias into the selection as galaxies with 
    certain structural properties are harder to detect than others. 
    \todo{Add average \s2n{} of the high and low \ser{} index galaxies at 
    $23.8 < i < 24.2$ mag.}
    Users of HSC survey data who want to select flux-limited samples of galaxies,
    or intend to study the population of faint (e.g. high-$z$) galaxies should
    keep this in mind.

    Similar to the synthetic stars, worse seeing condition can also lead to 
    noticeable decrease of \s2n{} at the same magnitude (see the figure for
    $i$-band). 
    Meanwhile, the highly blended synthetic galaxies do not show significantly 
    different \s2n{} distributions here.
